---
title: "I-Vax Game Analysis"
output: html_notebook
editor_options: 
  markdown: 
    wrap: 72
---

In this notebook we present the results of the implementation of the
analysis we conducted on our proof-of-concept implementation of the
interactive vaccination (I-Vax) game presented in our [paper](). We
refer to the paper for the discussion and presentation of the results.

```{r}
# Remove annoying warnings
options(warn=-1)

# Import libraries
library("plyr")
library("dplyr")
library("imputeTS")
library("lme4")

# For log odds from models
library("broom.mixed")

# For plots
library("ggeffects")
library("ggplot2")

# Survival
library("survival")
library("coxme")
```

# 1 Data Preparation

Let's prepare the data for the models, starting with the round (waves)
outcomes.

```{r}
# Read data
mydata14 <- read.table("Anonymized Data/end_of_wave_status_1-4.csv", header=TRUE, row.names='X', sep=",")
mydata14 <- mydata14[!duplicated(mydata14), ] # Remove duplicates if it's the case

mydata58 <- read.table("Anonymized Data/end_of_wave_status_5-8.csv", header=TRUE, row.names='X', sep=",")
mydata58 <- mydata58[!duplicated(mydata58), ] # Remove duplicates if it's the case

mydata912 <- read.table("Anonymized Data/end_of_wave_status_9-12.csv", header=TRUE, row.names='X', sep=",")
mydata912 <- mydata912[!duplicated(mydata912), ] # Remove duplicates if it's the case
```

Let's encode the states:

-   **I** **= 0** as well as **R** **= 0**, since they both represent
    the fact that the player got infected (even if recovered)

-   **V = 1** and **A = 1**, these are the cases where the user was
    vaccinated or still awaiting the vaccination

-   **S = 2**, susceptible players

```{r}
# Apply the function
mydata14['state'] <- lapply(mydata14['state'], function(x) mapvalues(x, c("I", "R", "V", "A", "S"), c(0, 0, 1, 1, 2)))
mydata58['state'] <- lapply(mydata58['state'], function(x) mapvalues(x, c("I", "R", "V", "A", "S"), c(0, 0, 1, 1, 2)))
mydata912['state'] <- lapply(mydata912['state'], function(x) mapvalues(x, c("I", "R", "V", "A", "S"), c(0, 0, 1, 1, 2)))
```

The next step is to transform the points to dummy points, to ease the
fit of the models:

-   **0** if there was no point loss

-   **1** if there was point loss

```{r}
# Function to map values
dummy_points <- function(points, state){
  res <- 0
  if(state == 0){ #Infected
    if(points == 100)
      res <- 0
    else
      res <- 1
  } else if (state == 1){ #Vaccinated
    if(points == 90)
      res <- 0
    else
      res <- 1
  } else if (state == 2){ #Susceptible
    res <- 0
  }
  
  return(res)
}

# Apply it
mydata14['points'] <- apply(mydata14[,c('points', 'state')], 1, function(x) dummy_points(as.integer(x[1]), as.integer(x[2])))
mydata58['points'] <- apply(mydata58[,c('points', 'state')], 1, function(x) dummy_points(as.integer(x[1]), as.integer(x[2])))
mydata912['points'] <- apply(mydata912[,c('points', 'state')], 1, function(x) dummy_points(as.integer(x[1]), as.integer(x[2])))

print(mydata14)
```

Next we have to combine the information from the subsequent waves to
have the correct factors. We will also add a control variable which
indicates which of the **feedback_setting** the round took place into (1
no feedback, 2 local feedback or 3 global feedback). Finally there will
be two distinct dataframes, one which contains data from all the the
rounds (that can therefore only be used without considering the
feedback) and the other with data from the rounds which had feedback.

```{r}
# Split data in waves
wave1 <- mydata14[mydata14['wave_no'] == 1,]
wave2 <- mydata14[mydata14['wave_no'] == 2,]
wave3 <- mydata14[mydata14['wave_no'] == 3,]
wave4 <- mydata14[mydata14['wave_no'] == 4,]
wave5 <- mydata58[mydata58['wave_no'] == 5,]
wave6 <- mydata58[mydata58['wave_no'] == 6,]
wave7 <- mydata58[mydata58['wave_no'] == 7,]
wave8 <- mydata58[mydata58['wave_no'] == 8,]
wave9 <- mydata912[mydata912['wave_no'] == 9,]
wave10 <- mydata912[mydata912['wave_no'] == 10,]
wave11 <- mydata912[mydata912['wave_no'] == 11,]
wave12 <- mydata912[mydata912['wave_no'] == 12,]

# Add feedback_setting
wave1['feedback_setting'] <- 1
wave2['feedback_setting'] <- 1
wave3['feedback_setting'] <- 1
wave4['feedback_setting'] <- 1
wave5['feedback_setting'] <- 2
wave6['feedback_setting'] <- 2
wave7['feedback_setting'] <- 2
wave8['feedback_setting'] <- 2
wave9['feedback_setting'] <- 3
wave10['feedback_setting'] <- 3
wave11['feedback_setting'] <- 3
wave12['feedback_setting'] <- 3

# Aggregate data for waves
train12 <- merge(wave1[c("user", "points", "state", "decision")], wave2[c("user", "wave_no", "decision", "feedback_setting")],
                 by="user", suffixes=c("_prev", ""))
train23 <- merge(wave2[c("user", "points", "state", "decision")], wave3[c("user", "wave_no", "decision", "feedback_setting")],
                 by="user", suffixes=c("_prev", ""))
train34 <- merge(wave3[c("user", "points", "state", "decision")], wave4[c("user", "wave_no", "decision", "feedback_setting")],
                 by="user", suffixes=c("_prev", ""))

train45 <- merge(wave4[c("user", "points", "state", "decision")], wave5[c("user", "wave_no", "decision", "feedback_setting")],
                 by="user", suffixes=c("_prev", ""))
train56 <- merge(wave5[c("user", "points", "state", "decision")], wave6[c("user", "wave_no", "decision", "feedback_setting")],
                 by="user", suffixes=c("_prev", ""))
train67 <- merge(wave6[c("user", "points", "state", "decision")], wave7[c("user", "wave_no", "decision", "feedback_setting")],
                 by="user", suffixes=c("_prev", ""))
train78 <- merge(wave7[c("user", "points", "state", "decision")], wave8[c("user", "wave_no", "decision", "feedback_setting")],
                 by="user", suffixes=c("_prev", ""))

train89 <- merge(wave8[c("user", "points", "state", "decision")], wave9[c("user", "wave_no", "decision", "feedback_setting")],
                 by="user", suffixes=c("_prev", ""))
train910 <- merge(wave9[c("user", "points", "state", "decision")], wave10[c("user", "wave_no", "decision", "feedback_setting")],
                  by="user", suffixes=c("_prev", ""))
train1011 <- merge(wave10[c("user", "points", "state", "decision")], wave11[c("user", "wave_no", "decision", "feedback_setting")],
                   by="user", suffixes=c("_prev", ""))
train1112 <- merge(wave11[c("user", "points", "state", "decision")], wave12[c("user", "wave_no", "decision", "feedback_setting")],
                   by="user", suffixes=c("_prev", ""))

# Concatenate all information
train112 <- rbind.fill(train12, train23, train34, train45, train56, train67, train78, train89, train910, train1011, train1112)
train512 <- rbind.fill(train45, train56, train67, train78, train89, train910, train1011, train1112)
```

## 1.1 EOW Feedback

Now let's include the EOW (end of wave) feedback. Wave number will be
increased by 1 since this information is going to be used in the
subsequent wave (e.g., `vaccinated_eow`).

```{r}
# Read feedback eow
eow_feedback5 <- read.table("Anonymized Data/wave5_feedback_eow.csv", header=TRUE, row.names='X', sep=",")
eow_feedback5['wave_no'] <- 6

eow_feedback6 <- read.table("Anonymized Data/wave6_feedback_eow.csv", header=TRUE, row.names='X', sep=",")
eow_feedback6['wave_no'] <- 7

eow_feedback7 <- read.table("Anonymized Data/wave7_feedback_eow.csv", header=TRUE, row.names='X', sep=",")
eow_feedback7['wave_no'] <- 8

eow_feedback8 <- read.table("Anonymized Data/wave8_feedback_eow.csv", header=TRUE, row.names='X', sep=",")
eow_feedback8['wave_no'] <- 9

eow_feedback9 <- read.table("Anonymized Data/wave9_feedback_eow.csv", header=TRUE, row.names='X', sep=",")
eow_feedback9['wave_no'] <- 10

eow_feedback10 <- read.table("Anonymized Data/wave10_feedback_eow.csv", header=TRUE, row.names='X', sep=",")
eow_feedback10['wave_no'] <- 11

eow_feedback11 <- read.table("Anonymized Data/wave11_feedback_eow.csv", header=TRUE, row.names='X', sep=",")
eow_feedback11['wave_no'] <- 12
```

We rename the columns, with \*\*\_eow\*\* being the suffix: this is
important because we are using both local and global feedback and in the
cumulative analysis we want to put them together. Moreover for the
global infected feedback we are going to have to add the recovered (they
were after all infected before recovering).

```{r}
# Wave 5
names(eow_feedback5)[names(eow_feedback5) == "vaccinated_interactions"] <- "vaccinated_eow"
names(eow_feedback5)[names(eow_feedback5) == "infected_interactions"] <- "infected_eow"
names(eow_feedback5)[names(eow_feedback5) == "recovered_interactions"] <- "recovered_eow"
names(eow_feedback5)[names(eow_feedback5) == "susceptible_interactions"] <- "susceptible_eow"

# Wave 6
names(eow_feedback6)[names(eow_feedback6) == "vaccinated_interactions"] <- "vaccinated_eow"
names(eow_feedback6)[names(eow_feedback6) == "infected_interactions"] <- "infected_eow"
names(eow_feedback6)[names(eow_feedback6) == "recovered_interactions"] <- "recovered_eow"
names(eow_feedback6)[names(eow_feedback6) == "susceptible_interactions"] <- "susceptible_eow"

# Wave 7
names(eow_feedback7)[names(eow_feedback7) == "vaccinated_interactions"] <- "vaccinated_eow"
names(eow_feedback7)[names(eow_feedback7) == "infected_interactions"] <- "infected_eow"
names(eow_feedback7)[names(eow_feedback7) == "recovered_interactions"] <- "recovered_eow"
names(eow_feedback7)[names(eow_feedback7) == "susceptible_interactions"] <- "susceptible_eow"

# Wave 8
names(eow_feedback8)[names(eow_feedback8) == "vaccinated_interactions"] <- "vaccinated_eow"
names(eow_feedback8)[names(eow_feedback8) == "infected_interactions"] <- "infected_eow"
names(eow_feedback8)[names(eow_feedback8) == "recovered_interactions"] <- "recovered_eow"
names(eow_feedback8)[names(eow_feedback8) == "susceptible_interactions"] <- "susceptible_eow"

# Wave 9
eow_feedback9$infected_all <- rowSums(eow_feedback9[, c("infected_all", "recovered_all")])
names(eow_feedback9)[names(eow_feedback9) == "vaccinated_all"] <- "vaccinated_eow"
names(eow_feedback9)[names(eow_feedback9) == "infected_all"] <- "infected_eow"
names(eow_feedback9)[names(eow_feedback9) == "recovered_all"] <- "recovered_eow"
names(eow_feedback9)[names(eow_feedback9) == "susceptible_all"] <- "susceptible_eow"

# Wave 10
eow_feedback10$infected_all <- rowSums(eow_feedback10[, c("infected_all", "recovered_all")])
names(eow_feedback10)[names(eow_feedback10) == "vaccinated_all"] <- "vaccinated_eow"
names(eow_feedback10)[names(eow_feedback10) == "infected_all"] <- "infected_eow"
names(eow_feedback10)[names(eow_feedback10) == "recovered_all"] <- "recovered_eow"
names(eow_feedback10)[names(eow_feedback10) == "susceptible_all"] <- "susceptible_eow"

# Wave 11
eow_feedback11$infected_all <- rowSums(eow_feedback11[, c("infected_all", "recovered_all")])
names(eow_feedback11)[names(eow_feedback11) == "vaccinated_all"] <- "vaccinated_eow"
names(eow_feedback11)[names(eow_feedback11) == "infected_all"] <- "infected_eow"
names(eow_feedback11)[names(eow_feedback11) == "recovered_all"] <- "recovered_eow"
names(eow_feedback11)[names(eow_feedback11) == "susceptible_all"] <- "susceptible_eow"

# Finally merge
eow_feedback512 <- rbind.fill(eow_feedback5, eow_feedback6, eow_feedback7, eow_feedback8, eow_feedback9, eow_feedback10, eow_feedback11)

print(eow_feedback512)
```

Since we are considering EOW feedback, we cannot consider wave 5: it has
no feedback coming from wave 4. Still we will need it to create the
survival data, so we will keep the information for now. Also, because of
the data gathering, there will be some missing values in the feedbacks:
these will be filled with the average value, so that their distribution
can remain as close as possible to the original. Having NAs for wave 5
won't change the mean outcome.

```{r}
# Merge the data so far with the EOW feedback
train_feedback512 <- merge(train512, eow_feedback512[c("user", "wave_no", "vaccinated_eow", "infected_eow", "recovered_eow", "susceptible_eow")],
                                               by=c("user", "wave_no"), suffixes=c("", "_day"), all.x=TRUE)

# Fill NAs of data
train_feedback512 <- na_mean(train_feedback512)

print(train_feedback512)
```

Lastly let's rescale the percentages of the feedback data to
probabilities (this will help in fitting the models).

```{r}
# Rescale with a for loop. The apply gave some problems
for(i in rownames(train_feedback512)) {
  train_feedback512[i, 8] <- train_feedback512[i, 8]/100
  train_feedback512[i, 9] <- train_feedback512[i, 9]/100
  train_feedback512[i, 10] <- train_feedback512[i, 10]/100
  train_feedback512[i, 11] <- train_feedback512[i, 11]/100
}

print(train_feedback512)
```

## 1.3 Round Number

For this analysis we want to see the impact of the feedback on the
various predictor. For this reason we have to aggregate the analogous
rounds (e.g. wave 1 with 5 and 9, wave 2 with 6 and 10 and so on...):
this will allow to really see the effect of the feedback setting. We
will have to do this for both the complete data and the data with
feedback.

```{r}
# Create new copies of the datasets
train112_ready <- train112
train512_ready <- train_feedback512

# Now apply the mapping
train112_ready['wave_no_en'] <- lapply(train112['wave_no'], function(x) mapvalues(x, c(5,6,7,8,9,10,11,12), c(1,2,3,4,1,2,3,4)))
train512_ready['wave_no_en'] <- lapply(train_feedback512['wave_no'], function(x) mapvalues(x, c(5,6,7,8,9,10,11,12), c(1,2,3,4,1,2,3,4)))
print(train512_ready)
```

## 1.4 Add Daily Feedback

We need to prepare the data for the survival analysis as well. We will
first need to read every feedback and rename the columns as before.

```{r}
# Read all feedback data
all_feedback5 <- read.table("Anonymized Data/wave5_every_feedback.csv", header=TRUE, row.names='X', sep=",")
all_feedback6 <- read.table("Anonymized Data/wave6_every_feedback.csv", header=TRUE, row.names='X', sep=",")
all_feedback7 <- read.table("Anonymized Data/wave7_every_feedback.csv", header=TRUE, row.names='X', sep=",")
all_feedback8 <- read.table("Anonymized Data/wave8_every_feedback.csv", header=TRUE, row.names='X', sep=",")
all_feedback9 <- read.table("Anonymized Data/wave9_every_feedback.csv", header=TRUE, row.names='X', sep=",")
all_feedback10 <- read.table("Anonymized Data/wave10_every_feedback.csv", header=TRUE, row.names='X', sep=",")
all_feedback11 <- read.table("Anonymized Data/wave11_every_feedback.csv", header=TRUE, row.names='X', sep=",")
all_feedback12 <- read.table("Anonymized Data/wave12_every_feedback.csv", header=TRUE, row.names='X', sep=",")
```

```{r}
# Wave 5
names(all_feedback5)[names(all_feedback5) == "vaccinated_interactions"] <- "vaccinated_surv"
names(all_feedback5)[names(all_feedback5) == "infected_interactions"] <- "infected_surv"
names(all_feedback5)[names(all_feedback5) == "recovered_interactions"] <- "recovered_surv"
names(all_feedback5)[names(all_feedback5) == "susceptible_interactions"] <- "susceptible_surv"

# Wave 6
names(all_feedback6)[names(all_feedback6) == "vaccinated_interactions"] <- "vaccinated_surv"
names(all_feedback6)[names(all_feedback6) == "infected_interactions"] <- "infected_surv"
names(all_feedback6)[names(all_feedback6) == "recovered_interactions"] <- "recovered_surv"
names(all_feedback6)[names(all_feedback6) == "susceptible_interactions"] <- "susceptible_surv"

# Wave 7
names(all_feedback7)[names(all_feedback7) == "vaccinated_interactions"] <- "vaccinated_surv"
names(all_feedback7)[names(all_feedback7) == "infected_interactions"] <- "infected_surv"
names(all_feedback7)[names(all_feedback7) == "recovered_interactions"] <- "recovered_surv"
names(all_feedback7)[names(all_feedback7) == "susceptible_interactions"] <- "susceptible_surv"

# Wave 8
names(all_feedback8)[names(all_feedback8) == "vaccinated_interactions"] <- "vaccinated_surv"
names(all_feedback8)[names(all_feedback8) == "infected_interactions"] <- "infected_surv"
names(all_feedback8)[names(all_feedback8) == "recovered_interactions"] <- "recovered_surv"
names(all_feedback8)[names(all_feedback8) == "susceptible_interactions"] <- "susceptible_surv"

# Wave 9
names(all_feedback9)[names(all_feedback9) == "vaccinated_all"] <- "vaccinated_surv"
names(all_feedback9)[names(all_feedback9) == "infected_all"] <- "infected_surv"
names(all_feedback9)[names(all_feedback9) == "recovered_all"] <- "recovered_surv"
names(all_feedback9)[names(all_feedback9) == "susceptible_all"] <- "susceptible_surv"

# Wave 10
names(all_feedback10)[names(all_feedback10) == "vaccinated_all"] <- "vaccinated_surv"
names(all_feedback10)[names(all_feedback10) == "infected_all"] <- "infected_surv"
names(all_feedback10)[names(all_feedback10) == "recovered_all"] <- "recovered_surv"
names(all_feedback10)[names(all_feedback10) == "susceptible_all"] <- "susceptible_surv"

# Wave 11
names(all_feedback11)[names(all_feedback11) == "vaccinated_all"] <- "vaccinated_surv"
names(all_feedback11)[names(all_feedback11) == "infected_all"] <- "infected_surv"
names(all_feedback11)[names(all_feedback11) == "recovered_all"] <- "recovered_surv"
names(all_feedback11)[names(all_feedback11) == "susceptible_all"] <- "susceptible_surv"

# Wave 12
names(all_feedback12)[names(all_feedback12) == "vaccinated_all"] <- "vaccinated_surv"
names(all_feedback12)[names(all_feedback12) == "infected_all"] <- "infected_surv"
names(all_feedback12)[names(all_feedback12) == "recovered_all"] <- "recovered_surv"
names(all_feedback12)[names(all_feedback12) == "susceptible_all"] <- "susceptible_surv"

# Merge them all
all_feedback512 <- rbind.fill(all_feedback5, all_feedback6, all_feedback7, all_feedback8, all_feedback9, all_feedback10, all_feedback11, all_feedback12)
all_feedback512 <- na_mean(all_feedback512)
```

For the survival analysis we want to have only one feedback per user per
wave. This means that for the vaccinated it's easy, since we'll just
keep the day in which they vaccinated (where there is the feedback of
the day before). For the non-vaccinated, instead, we will keep the last
day of the week, as it was the last occasion they had to vaccinate
(after that there is **censoring** and it's important to consider this
data).

```{r}
# Divide between vaccinated and non-vaccinated
all_feedback512_vax <- all_feedback512[all_feedback512['vaccinated']==1, ]
all_feedback512_inf <- all_feedback512[all_feedback512['is_infected']==1, ]
all_feedback512_novax <- all_feedback512[(all_feedback512['vaccinated']==0) & (all_feedback512['is_infected']==0), ]

# Remove duplicates from vaccinated keeping only the first day (default distinct behaviour)
all_feedback512_nodup <- distinct(.data=all_feedback512_vax, user, wave_no, .keep_all=TRUE)

# Do the same with infected
all_feedback512_nodup_inf <- distinct(.data=all_feedback512_inf, user, wave_no, .keep_all=TRUE)

# Remove the unnecessary entries for non-vaccinated
# The infected and vaccinated that might be here will not be here anymore, as all the days before vaccination/infection are removed with this
novax <- all_feedback512_novax[all_feedback512_novax['day']==7, ]

# Put them together again
train_surv512 <- rbind.fill(novax, all_feedback512_nodup, all_feedback512_nodup_inf)

print(train_surv512)
```

As last step we need now to merge this with the previous information
(wave outcome and EOW feedback).

```{r}
# Keep only the relevant information from surv
# Keep survival feedback for wave 5 as well
train_surv512 <- merge(train_surv512[c("user", "wave_no", "day", "vaccinated_surv", "infected_surv", "recovered_surv", "susceptible_surv")],
                       train512_ready, by=c("user", "wave_no"), suffixes=c("", "_day"))

# Make percentages probabilities
for(i in rownames(train_surv512)) {
  train_surv512[i, 4] <- train_surv512[i, 4]/100
  train_surv512[i, 5] <- train_surv512[i, 5]/100
  train_surv512[i, 6] <- train_surv512[i, 6]/100
  train_surv512[i, 7] <- train_surv512[i, 7]/100
}


print(train_surv512)
```

## 1.5 Make Variables Categorical

Now we need to transform the variable that are not numerical into
categorical. This is theoretically more correct and will allow to see
directly from the model the difference between a baseline condition and
the possible different values of the covariates.

The ones we can make categorical are: **points** (point loss and no
loss), **decision_prev** (vaccination or no vaccination) and
**feedback_setting**. The outcome will stay as it is as the logistic
model allows us to predict the probability towards vaccination. We will
also order these categories, because when training the models R takes
the first one as the baseline to compare the others.

Instead, for what regards **decision** we want to leave it numerical: in
this way the model will treat it like probabilities and return us the
probability of getting vaccinated.

```{r}
# WHOLE DATASET
train112_readyc <- train112_ready

# Handle points
train112_readyc$points[train112_readyc['points']==1] <- "Loss"
train112_readyc$points[train112_readyc['points']==0] <- "NoLoss"

# Handle decision_prev
train112_readyc$decision_prev[train112_readyc['decision_prev']==1] <- "Vaccination"
train112_readyc$decision_prev[train112_readyc['decision_prev']==0] <- "NoVaccination"

# Handle feedback_setting
train112_readyc$feedback_setting[train112_readyc['feedback_setting']==1] <- "NoFeedback"
train112_readyc$feedback_setting[train112_readyc['feedback_setting']==2] <- "Local"
train112_readyc$feedback_setting[train112_readyc['feedback_setting']==3] <- "Global"

# Also order the values
train112_readyc$points = factor(train112_readyc$points, levels=c("NoLoss", "Loss"))
train112_readyc$decision_prev = factor(train112_readyc$decision_prev, levels=c("NoVaccination", "Vaccination"))
train112_readyc$feedback_setting = factor(train112_readyc$feedback_setting, levels=c("NoFeedback", "Local", "Global"))

print(train112_readyc)
```

```{r}
# SETTINGS WITH FEEDBACK (For Survival)
train512_readyc <- train_surv512

# Handle points
train512_readyc$points[train512_readyc['points']==1] <- "Loss"
train512_readyc$points[train512_readyc['points']==0] <- "NoLoss"

# Handle decision_prev
train512_readyc$decision_prev[train512_readyc['decision_prev']==1] <- "Vaccination"
train512_readyc$decision_prev[train512_readyc['decision_prev']==0] <- "NoVaccination"

# Handle feedback_setting
train512_readyc$feedback_setting[train512_readyc['feedback_setting']==1] <- "NoFeedback"
train512_readyc$feedback_setting[train512_readyc['feedback_setting']==2] <- "Local"
train512_readyc$feedback_setting[train512_readyc['feedback_setting']==3] <- "Global"

# Also order the values
train512_readyc$points = factor(train512_readyc$points, levels=c("NoLoss", "Loss"))
train512_readyc$decision_prev = factor(train512_readyc$decision_prev, levels=c("NoVaccination", "Vaccination"))
train512_readyc$feedback_setting = factor(train512_readyc$feedback_setting, levels=c("NoFeedback", "Local", "Global"))

print(train512_readyc)
```

## 1.6 Center Variables

Since we are treating some predictors that could've been problematic as
categorical, it is now possible to center the other variables. This
should allow for a better fit of the models, meaning better capturing of
the significant effects.

**Group mean centering** would be ideal in a setting with random
effects, but there are not enough measurements for each user. We will
then use **grand mean centering**, which only consists in subtracting
the overall mean of the variable to each of its values (but at a
feedback condition level).

```{r}
# For survival feedback
vax_surv_mean2 <- mean(train512_readyc[train512_readyc['feedback_setting']==2,][['vaccinated_surv']], na.rm=TRUE)
vax_surv_mean3 <- mean(train512_readyc[train512_readyc['feedback_setting']==3,][['vaccinated_surv']], na.rm=TRUE)
inf_surv_mean2 <- mean(train512_readyc[train512_readyc['feedback_setting']==2,][['infected_surv']], na.rm=TRUE)
inf_surv_mean3 <- mean(train512_readyc[train512_readyc['feedback_setting']==3,][['infected_surv']], na.rm=TRUE)
susc_surv_mean2 <- mean(train512_readyc[train512_readyc['feedback_setting']==2,][['susceptible_surv']], na.rm=TRUE)
susc_surv_mean3 <- mean(train512_readyc[train512_readyc['feedback_setting']==3,][['susceptible_surv']], na.rm=TRUE)

# For EOW feedback
vax_eow_mean2 <- mean(train512_readyc[train512_readyc['feedback_setting']==2,][['vaccinated_eow']], na.rm=TRUE)
vax_eow_mean3 <- mean(train512_readyc[train512_readyc['feedback_setting']==3,][['vaccinated_eow']], na.rm=TRUE)
inf_eow_mean2 <- mean(train512_readyc[train512_readyc['feedback_setting']==2,][['infected_eow']], na.rm=TRUE)
inf_eow_mean3 <- mean(train512_readyc[train512_readyc['feedback_setting']==3,][['infected_eow']], na.rm=TRUE)
susc_eow_mean2 <- mean(train512_readyc[train512_readyc['feedback_setting']==2,][['susceptible_eow']], na.rm=TRUE)
susc_eow_mean3 <- mean(train512_readyc[train512_readyc['feedback_setting']==3,][['susceptible_eow']], na.rm=TRUE)

# Subtract the mean from each element
train512_readyc[train512_readyc['feedback_setting']==2,]['vaccinated_surv'] <- sapply(train512_readyc[train512_readyc['feedback_setting']==2,]['vaccinated_surv'], function(x) x - vax_surv_mean2)
train512_readyc[train512_readyc['feedback_setting']==3,]['vaccinated_surv'] <- sapply(train512_readyc[train512_readyc['feedback_setting']==3,]['vaccinated_surv'], function(x) x - vax_surv_mean3)

train512_readyc[train512_readyc['feedback_setting']==2,]['infected_surv'] <- sapply(train512_readyc[train512_readyc['feedback_setting']==2,]['infected_surv'], function(x) x - inf_surv_mean2)
train512_readyc[train512_readyc['feedback_setting']==3,]['infected_surv'] <- sapply(train512_readyc[train512_readyc['feedback_setting']==3,]['infected_surv'], function(x) x - inf_surv_mean3)

train512_readyc[train512_readyc['feedback_setting']==2,]['susceptible_surv'] <- sapply(train512_readyc[train512_readyc['feedback_setting']==2,]['susceptible_surv'], function(x) x - susc_surv_mean2)
train512_readyc[train512_readyc['feedback_setting']==3,]['susceptible_surv'] <- sapply(train512_readyc[train512_readyc['feedback_setting']==3,]['susceptible_surv'], function(x) x - susc_surv_mean3)

# EOW
train512_readyc[train512_readyc['feedback_setting']==2,]['vaccinated_eow'] <- sapply(train512_readyc[train512_readyc['feedback_setting']==2,]['vaccinated_eow'], function(x) x - vax_eow_mean2)
train512_readyc[train512_readyc['feedback_setting']==3,]['vaccinated_eow'] <- sapply(train512_readyc[train512_readyc['feedback_setting']==3,]['vaccinated_eow'], function(x) x - vax_eow_mean3)

train512_readyc[train512_readyc['feedback_setting']==2,]['infected_eow'] <- sapply(train512_readyc[train512_readyc['feedback_setting']==2,]['infected_eow'], function(x) x - inf_eow_mean2)
train512_readyc[train512_readyc['feedback_setting']==3,]['infected_eow'] <- sapply(train512_readyc[train512_readyc['feedback_setting']==3,]['infected_eow'], function(x) x - inf_eow_mean3)

train512_readyc[train512_readyc['feedback_setting']==2,]['susceptible_eow'] <- sapply(train512_readyc[train512_readyc['feedback_setting']==2,]['susceptible_eow'], function(x) x - susc_eow_mean2)
train512_readyc[train512_readyc['feedback_setting']==3,]['susceptible_eow'] <- sapply(train512_readyc[train512_readyc['feedback_setting']==3,]['susceptible_eow'], function(x) x - susc_eow_mean3)

print(head(train512_readyc,10))
```

# 2 Mixed Effects Analysis

Here we will analyze the impact of the feedback on the predictors that
are common to all feedback settings. This analysis is centered on
**self-effects**, meaning that the decision is predicted from
information about the individual player.

## 2.1 Behaviour Given Individual Outcome in Previous Round

Here we predict users' **decision** given the other effects. We use
**user** as random effect, to group the observation of the participants.

We also want to introduce a **link function**: the outcome is binary so
it will be a **logistic link**, which will help to transform the linear
result into a probability.

This model is reported in the original paper in **TABLE 1** and
commented in **Section 2.1.**

```{r}
feedbackImpact <- glmer(decision~(1|user)+points+decision_prev+points:decision_prev+wave_no_en+feedback_setting,
                       data=train112_readyc, family=binomial(link="logit"),control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(feedbackImpact)
print(tidy(feedbackImpact,conf.int=TRUE,exponentiate=TRUE,effects="fixed"))
```

Before analyzing we have to say that since we have categorical values,
we have a combination of these values used as baseline. The combination
is such that the baseline is the following: `points=0` (no loss),
`decision_prev=0` (no vaccination), `feedback_setting=1` (no feedback).
We have the **intercept** representing this setting.

The coefficient are pretty self explanatory. Once again we refer to the
paper for an in-depth explanation.

We have the **points:decision_prev** interaction being significant and
negative. This will be across all the analysis the most important effect
and we show what happens with the following plot. This is FIGURE 1 of
the paper.

```{r}
# Your existing code for generating the plot
plot_data <- ggpredict(feedbackImpact, c("points", "decision_prev"), alpha = 0.05)

# Create the plot with error bar caps and dodge positioning
ggplot(plot_data, aes(x = factor(x, levels = unique(x)), y = predicted, ymin = conf.low, ymax = conf.high, color = as.factor(group))) +
  geom_point(position = position_dodge(width = 0.5), size = 3) +
  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    position = position_dodge(width = 0.5),
    width = 0.2  # Adjust the width of the error bars
  ) +
  ggtitle("Vaccination probabilities given Points and Previous Decision") +
  ylab("Vaccination Probability") +
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  xlab("Points") +
  labs(color="Previous Decision") +
  #scale_color_manual(values=c("red", "blue")) +
  theme(legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.line = element_line(),
    axis.ticks = element_line() #colour = "grey"
  )
```

As we can see from the plot it is very clear that the interaction is
mostly significant when there was no point loss: if the player did
vaccinate in the previous wave the probability of vaccinating again is
pretty high, while for if he did not vaccinate the probability is very
low (and also with a very small variability). When there was point loss,
instead, there is no substantial difference depending on the previous
decision.

## 2.2 Behaviour Given Environmental Feedback

Here we will look at the impact of the feedback given to players at the
end of the rounds (on the number of vaccinated, infected, recovered
individuals).

We will take the model from Section 2.1 and add the **EOW Feedback**
(end-of-wave feedback). These feedback will also have an interaction
with **feedback_setting**, so to control for the *Global* and *Local*
feedback conditions. We also need to exclude wave 5, as there was no EOW
feedback coming from wave 4.

This model is reported in the original paper in **TABLE 2** and
commented in **Section 2.2.**

```{r}
# Create train for EOW feedback
train612_readyc <- train512_readyc[train512_readyc['wave_no']>5,]

completeModel <- glmer(decision~(1|user)+points+decision_prev+points:decision_prev+wave_no_en+feedback_setting+vaccinated_eow+
                         infected_eow+susceptible_eow+vaccinated_eow:feedback_setting+infected_eow:feedback_setting+susceptible_eow:feedback_setting,
                       data=train612_readyc, family=binomial(link="logit"),control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(completeModel)
print(tidy(completeModel,conf.int=TRUE,exponentiate=TRUE,effects="fixed"))
```

We see again the impact of the interaction between previous decision,
while the environmental feedback did not have a significant impact.

# 3 Survival Analysis

In this section we want to investigate the **daily feedback**. The best
way to do so is through survival analysis: it allows to model scenarios
in which there is an event that can happen or not to the subjects
(usually death, that's why survival) and thus uses the effects to model
how many survive. In this scenario we will set ***Vaccination*** as the
decision corresponding to the event of the models. They also take into
account time and for this, since we look at the daily feedback, we'll
use the days within waves.

## 3.1 Behaviour Given Daily Feedback

For how the `coxme` library works we now need to encode
**feedback_setting** so that it only has two values and not all three.
*Local* will be the baseline again, as in Section 4.1. Also, let's only
get the data from day 2 (as in day 1 players did not see any daily
feedback previously).

```{r}
# Data from day 2
train512_readyc_noday1 <- train512_readyc[train512_readyc['day']>1,]

# Encode feedback setting with only 2 values
train512_readyc_noday1$feedback_setting <- factor(train512_readyc_noday1$feedback_setting, levels=c("Local", "Global"))
```

```{r}
train512_readyc_noday1
```

```{r}
# Go back to percentages. Does not change the model, but easier plots

for(i in rownames(train512_readyc_noday1)) {
  train512_readyc_noday1[i, 4] <- train512_readyc_noday1[i, 4]*100
  train512_readyc_noday1[i, 5] <- train512_readyc_noday1[i, 5]*100
  train512_readyc_noday1[i, 6] <- train512_readyc_noday1[i, 6]*100
  train512_readyc_noday1[i, 7] <- train512_readyc_noday1[i, 7]*100
}
```

We can also use `coxph` which is just a different implementation, but it
is easier to use to plot the data. The data reported in the paper in
TABLE 3 is actually the `coxph` model.

```{r}
cox_feedback <- coxme(Surv(day, decision) ~ (1|user)+points+decision_prev+points:decision_prev+feedback_setting+vaccinated_surv+wave_no_en+
                        infected_surv+susceptible_surv+feedback_setting:vaccinated_surv+feedback_setting:infected_surv+feedback_setting:susceptible_surv,
                      data=train512_readyc_noday1)
summary(cox_feedback)
confint(cox_feedback, level = 0.95)
```

```{r}
cox_feedback_asd <- coxph(Surv(day, decision) ~ frailty(user)+points+decision_prev+points:decision_prev+feedback_setting+vaccinated_surv+wave_no_en+
                        infected_surv+susceptible_surv+feedback_setting:vaccinated_surv+feedback_setting:infected_surv+feedback_setting:susceptible_surv,
                      data=train512_readyc_noday1)
summary(cox_feedback_asd)
```

Now let's get the confidence intervals for the model.

```{r}
# Confidence Intervals
confint(cox_feedback_asd)
```

Finally, let's plot the most interesting interaction, meaning the one
between the feedback setting and the susceptible daily feedback. This is
FIGURE 2 of the paper. The figure below also puts the ribbon for the 95%
CI, but it hinders the readability of the plot.

```{r}
data_plt_inf <- ggpredict(cox_feedback_asd, c("susceptible_surv", "feedback_setting"))

# Create the plot
ggplot(data_plt_inf, aes(x = x, y = predicted)) +
  geom_line(aes(color = group)) +
  ylab("Hazard Ratio") +
  xlab("Percentage of Susceptible") +
  #scale_y_continuous(limits = c(0, 0.0005)) +# if you want to cut the plot
  #scale_y_log10() + # If you want the plot in logscale
  scale_color_discrete(name = "Feedback Setting") +
  theme_minimal() +  # Use a minimal theme
  theme(legend.position = "bottom",  # Move the legend to the bottom
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(),
        axis.ticks = element_line())+
  coord_cartesian(ylim = c(min(data_plt_inf$predicted), max(0.0005)))  # Set y-axis limit without removing data points

#ggsave("Plots/daily_susc.png", width = 6, height = 4, dpi = 300)
```

```{r}
# Create the plot
ggplot(data_plt_inf, aes(x = x, y = predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.2, show.legend = FALSE) +
  geom_line(aes(color = group)) +
  ylab("Hazard Ratio") +
  xlab("Percentage of Susceptible") +
  scale_y_log10() +
  scale_color_discrete(name = "Feedback Setting") +
  theme_minimal() +  # Use a minimal theme
  theme(legend.position = "bottom",  # Move the legend to the bottom
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(),
        axis.ticks = element_line())

#ggsave("Plots/daily_susc_err.png", width = 6, height = 4, dpi = 300)
```
